Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex

\subsection{Results}
\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
fraction of users will encounter major usability obstacles. However, it was effective at discovering 
and demonstrating issues that are likely to cause problems for many users. 
People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
code-signing feature on OS X), did not understand what many of the toolbar options meant, 
and were confused by most Tor-specific behaviors. For specific problems 
encountered by an individual user, we refer you to our resources below.

{\color {red}

We saw an SEO poisoning opportunity.

\begin{quote}{\it
``I'm going to use Chrome, because that's what I use at home\ldots\ 
I'm just going to open it up, and I'm going to type in `download tor' because 
that's what I'm supposed to do. And I'm going to click on the first one, because,
at the top, which is `Download Tor'.''} \mbox{---P}
\end{quote}

@@

\begin{quote}{\it
``There's, like, the first thing on the page is called the Tor Project, and I wouldn't figure out what that is,
but then it says `Tor Browser' just a little bit underneath, so I get, I put two and two together and I figure 
this is probably what I have to download.'}' \mbox{---P3}
\end{quote}

\begin{quote}{\it
``\ldots so I am going to type in `tor mac download'.
And that gives me some suggestions. I pick the first one.''} \mbox{---P4}
\end{quote}

@@

\begin{quote}{\it
``So yeah, there was an onion. Small green onion. And yeah, I guess, it's new identity.
So I'm guessing it's the same thing as with Google, when you open a page and you don't 
want the history to show up or something. And then you can, it's like you're disconnected 
from your Gmail account and everything, you can type that as a different user.''} \mbox{---P3} 
\end{quote}
}

>>>>

\subsection{Results}
\indent \indent This experiment uncovered a powerful vector for attack, an unlikely source
of usability issues, and insight into how to better communicate to users so that they can be 
empowered to use Tor Browser and its advanced settings. 
Because of the limited size of the study, it's not possible to state with confidence what 
fraction of users will encounter major usability obstacles. However, it was effective at discovering 
and demonstrating issues that are likely to cause problems for many users. 
People did have difficulty with installing Tor Browser (principally because of the Gatekeeper 
code-signing feature on OS X), did not understand what many of the toolbar options meant, 
and were confused by most Tor-specific behaviors. For specific problems 
encountered by an individual user, we refer you to our resources online.

\subsubsection{How to Attack Users}
During the task completion process, we observed that all our participants are likely 
susceptible to a search engine optimization (SEO) poisoning attack. Most of our 
participants  were on autopilot to complete this standard download task and 
were also not aware of the possibility that their download may come from an 
illegitimate source. Usually, our participants picked whichever was the first search
result and believed it to be a good enough source for the download:

\begin{quote}{\it
``I'm going to use Chrome, because that's what I use at home\ldots\ 
I'm just going to open it up, and I'm going to type in `download tor' because 
that's what I'm supposed to do. And I'm going to click on the first one, because,
at the top, which is `Download Tor'.''}\mbox{---P1}
\end{quote}

@@

There was one participant who did not pick the first search result, but to save themselves
time while completing the task: 
\begin{quote}{\it
``\ldots so I am going to type in `tor mac download'.
And that gives me some suggestions. I pick the first one.''} \mbox{---P4}
\end{quote}

@@

\begin{quote}{\it
``So yeah, there was an onion. Small green onion. And yeah, I guess, it's new identity.
So I'm guessing it's the same thing as with Google, when you open a page and you don't 
want the history to show up or something. And then you can, it's like you're disconnected 
from your Gmail account and everything, you can type that as a different user.''} \mbox{---P3} 
\end{quote}
